Fast Bayesian Inference for Exoplanet Discovery in Radial Velocity Data

### 2014-12-13 Paper/ms.tex
More words about sampling distribution

\section{Inference}
Bayesian inference is the use of probability theory to describe uncertainty
\citep{sivia, ohagan}. In this framework, we approach data analysis problems by first
constructing a {\it hypothesis space}, which is the set of possible answers
to the problem we are considering. Normally, this is the set of possible
values of a vector of parameters $\theta$ whose values we want
to know. We then assign probability distributions
called the {\it prior} and the {\it sampling distribution}. The prior
distribution $p(\theta)$ describes
our initial uncertainty about which values of the parameters
$\theta$ are plausible, and the
sampling distribution $p(D | \theta)$ describes
our initial uncertainty about the data set we're going to observe, as a
function of the unknown parameters $\theta$.
When the data is known, our state of knowledge about the parameter is
updated from the prior $p(\theta)$ to the posterior distribution given by
Bayes' rule:
\begin{eqnarray}
p(\theta | D) &=&
\frac{p(\theta)p(D | \theta)}
{p(D)}
\end{eqnarray}
where $p(D | \theta)$ is called the likelihood, once the actual dataset
is substituted in.
The denominator, often called the {\it evidence} or
{\it marginal likelihood}, is given by the expected value of the likelihood
with respect to the prior:
\begin{eqnarray}
\mathcal{Z} = p(D) = \int p(\theta) p(D | \theta) d^n \theta
\end{eqnarray}
where the integral is over the entire $n$-dimensional parameter space.
In the context of Bayesian computation, the prior is often denoted $\pi(\theta)$,
the likelihood $L(\theta)$, and the marginal likelihood $\mathcal{Z}$.

>>>>

\section{Inference}
Bayesian inference is the use of probability theory to describe uncertainty
\citep{sivia, ohagan}. In this framework, we approach data analysis problems by first
constructing a {\it hypothesis space}, which is the set of possible answers
to the problem we are considering. Normally, this is the set of possible
values of a vector of parameters $\theta$ whose values we want
to know. We then assign probability distributions
called the {\it prior} and the {\it sampling distribution}. The prior
distribution $p(\theta)$ describes
our initial uncertainty about which values of the parameters
$\theta$ are plausible, and the
sampling distribution $p(D | \theta)$ describes
our initial uncertainty about the data set we're going to observe, as a
function of the unknown parameters $\theta$.
When the data is known, our state of knowledge about the parameter is
updated from the prior $p(\theta)$ to the posterior distribution given by
Bayes' rule:
\begin{eqnarray}
p(\theta | D) &=&
\frac{p(\theta)p(D | \theta)}
{p(D)}
\end{eqnarray}
where $p(D | \theta)$ is called the likelihood, once the actual dataset
is substituted in. Note that some authors do not distinguish between a
sampling distribution and a likelihood. Throughout this paper we use the term
sampling distribution for $p(D|\theta)$ if we are discussing a probability
distribution (actually a family of them, indexed by $\theta$)
over the set of possible datasets. We use the term {\it likelihood}
when the actual dataset has been plugged in, when $p(D|\theta)$
becomes a scalar function (not a probability distribution)
over the parameter space.

The denominator, often called the {\it evidence} or
{\it marginal likelihood}, is given by the expected value of the likelihood
with respect to the prior:
\begin{eqnarray}
\mathcal{Z} = p(D) = \int p(\theta) p(D | \theta) d^n \theta
\end{eqnarray}
where the integral is over the entire $n$-dimensional parameter space.
In the context of Bayesian computation, the prior is often denoted $\pi(\theta)$,
the likelihood $L(\theta)$, and the marginal likelihood $\mathcal{Z}$.
